---
title: "02-tsgraphics"
author: "Alison Hill"
date: "July 2, 2018"
output: html_document
---

```{r eval = FALSE}
install.packages('fpp2', dependencies = TRUE)
# install.packages("devtools")
devtools::install_github("robjhyndman/fpp2-package")
```

Note: I'm wondering if [`tibbletime`](https://business-science.github.io/tibbletime/) might also be a useful package for us (check out vignettes!)

```{r}
library(fpp2)
```

This loads `ggplot2` and `forecast`.

```{r}
autoplot(melsyd[,"Economy.Class"]) +
  ggtitle("Economy class passengers: Melbourne-Sydney") +
  xlab("Year") +
  ylab("Thousands")
```

`autoplot` function sort of just thrown at us. I'm guessing it is loaded in the `fpp2` package? Nope- looks like mainly data in there: https://github.com/robjhyndman/fpp2-package/tree/master/man

OK google says the `ggfortify` package:
https://cran.r-project.org/web/packages/ggfortify/vignettes/plot_ts.html
```{r}
library(ggfortify)
```

Nope! You can do `?autoplot` and one of the options is from the `ggplot2` package. Help docs say (using `printr` from [Yihui](https://yihui.name/printr/)):

```{r}
library(printr)
# ??autoplot
help.search('autoplot', package = 'ggplot2')
```

So it is available because `fpp2` loads `ggplot2`. Moving on 😉

