---
title: "dc-ch1-notes"
author: "Alison Hill"
date: "7/27/2018"
output: html_document
---

This course: only regularly spaced interval time series

Definition: forecasting the method for estimating how a sequence of observations will continue into the future.

## Creating a `ts` object

Note: this part seems relatively easy, it's the other way that is a PITA.

In the sample code, `=` is used as the assignment operator (I think?)

I guess we assume this data is sorted by date already?

You also need to know to use the colon operator to select a range of columns by position.

## Time series plots

That *damn* `autoplot` function again! I think it needs to be said it is in the `ggplot2` package, since there are several same-named functions.

May pull up this data from `forecast`:

- `gold` containing gold prices in US dollars
- `woolyrnq` containing information on the production of woollen yarn in Australia
- `gas` containing Australian gas production

```{r}
library(forecast)
```

Oh ok `autoplot` with `facets = TRUE` expects multiple time series "streams", so they all get stacked on top of each other. So, data doesn't have to be "tidy" to facet.

```{r}
autoplot(gold)
autoplot(woolyrnq)
autoplot(gas)
```


The `frequency()` function returns the number of observations per unit time.

```{r}
frequency(gold)
frequency(woolyrnq)
frequency(gas)
```


## Seasonal plots

Text: https://otexts.org/fpp2/seasonal-plots.html
https://otexts.org/fpp2/seasonal-subseries-plots.html


Ooh `ggseasonplot()`?

Data from `fpp2`: `a10` and `ausbeer`

```{r}
library(fpp2)
autoplot(a10)
ggseasonplot(a10)
ggseasonplot(a10, polar = TRUE)
```

Looks like this is how one `filter`s on time:
```{r}
# Restrict the ausbeer data to start in 1992
beer <- window(ausbeer, start = 1992)

# Make plots of the beer data
autoplot(beer)
ggsubseriesplot(beer)
```

# Time series patterns

Text: https://otexts.org/fpp2/tspatterns.html

Trends are long-term
Seasonality refers to periodic patterns
Cyclic patterns



## Autocorrelation of non-seasonal time series

Text: https://otexts.org/fpp2/lag-plots.html
https://otexts.org/fpp2/autocorrelation.html

`oil` from `fpp2`

```{r}
# Create an autoplot of the oil data
autoplot(oil)

# Create a lag plot of the oil data
gglagplot(oil)

# Create an ACF plot of the oil data
ggAcf(oil)
```

What the heck am I looking at?

Last plot I think y-axis is strength of correlation, imaginary range -1 to 1. Height of sticks is just showing me the number. I don't know what the blue lines are? Read docs, still don't know. Ah:
https://stats.stackexchange.com/questions/49571/understanding-the-blue-dotted-lines-in-an-acf-from-r

From text now I found the section:
"The dashed blue lines indicate whether the correlations are significantly different from zero."

If "All of the autocorrelation coefficients lie within these limits, confirming that the data are white noise."

Oh ok later on in "white noise" video, this gets explained.

## Autocorrelation of seasonal and cyclic time series

Data:
https://stat.ethz.ch/R-manual/R-devel/library/datasets/html/sunspot.year.html

```{r}
# Plot the annual sunspot numbers
autoplot(sunspot.year)
ggAcf(sunspot.year)
```

Ah this exercise totally confused me- you are not expected to calculate the maximum lag using r, but rather just eyeball the value of the lag on the x-axis associated with max y, then enter that as a constant. Weird?

The next mc exercise was a little like "what"? So far I've been looking at plots and hoping we'll get to interpret, so I just kept guessing.

# White noise

## Stock prices and white noise

new `diff` function does what in this context? oh right lagged differences, base version of `dplyr::lag`.


