---
title: "eve-online-data"
author: "Alison Hill"
date: "July 23, 2018"
output: html_document
---

```{r}
library(googledrive)
drive_auth(oauth_token = NULL)
```

```{r}
drive_find(q = "fullText contains 'navitron_navitron-system-stats_2018-07-17.csv'")
```

```{r}
eve_id <- as_id("https://drive.google.com/open?id=1dD9zly6mD51IX79O3Tg1hwfqGskExQvt")
eve <- drive_download(file = eve_id, path = "eve_dump.csv")
```

other 3 ones:

* sde-universe_2018-07-16.csv
* navitron_navitron-server-status_2018-07-17.csv

```{r}
library(tidyverse)
eve_dump <- read_csv("eve_dump.csv")
```

npc_kills = non-player combatant
ship_kills = you can to blow up others' ships (hard)
ship_jumps = number of ships that entered in the last hour (but updated every 15 min)
pod_kills = you want to blow up others' ships + escape pods (harder)
system_id = unique identifier (geographic region within the game)

every combination of cron_datetime + system_id is a unique row
cron_datetime is every 15 min

```{r}
eve_dump <- eve_dump %>% 
  arrange(cron_datetime) %>% 
  group_by(system_id) %>% 
  mutate(dt_diff = cron_datetime - lag(cron_datetime))
```

filter on system_id 30002718- "a lot of pirates hang out here"
A system you expect a high number of kills, a lot of cyclic behavior

```{r}
eve_rancer <- eve_dump %>% 
  filter(system_id == "30002718")
```

```{r}
ggplot(eve_rancer, aes(x = cron_datetime, y = ship_kills)) +
  geom_line() 
```

focus in on one week, one month plots
```{r}
eve_rancer %>% 
  filter(cron_datetime > "2018-07-01") %>% 
  ggplot(., aes(x = cron_datetime, y = ship_kills)) +
  geom_line() 
```

what to do with those missing hours?

```{r}
library(lubridate)
want_rancer <- eve_rancer %>%  
  ungroup() %>%
  mutate(time_stamp = round_date(cron_datetime, unit = "hour")) %>% 
  complete(nesting(system_id), 
           time_stamp = seq(min(time_stamp), max(time_stamp), 
                      by = "hour"))
```

